Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2015-05-15 tex/scam/reviews-v1/response-v1.tex

%\item \rc{On page 47, ``a sub-exponential random is''.}

\end{enumerate}

\subsection*{Reviewer 3}

\begin{enumerate}

\item \rc{I don't see why one would use convex regression to do
  variable screening when other parametric approaches seem more
  appropriate (e.g. clean and screen methods by Ke et al. and
  others). This method and others were compared with and so it again
  raised the question of what class of interesting examples would this
  method be useful for.}

Our methods are appropriate in settings where one expects the
regression function to be convex, for example in utility function
estimation in economics. The power of our results is that
using convex additive models results in consistent variable selection.
In more general settings, without this shape constraint,
approaches based on the lasso (``screen and clean'') or nonparametric 
additive models do not have such guarantees.

Also note that we have replaced the multivariate Gaussian examples with 
nonparametric examples; please see point 3 below.

\item \rc{The basis of all the results seem to be the boundary flatness
condition. This condition seems to be an artifact of the analysis and
based on my reading, it is unclear how restrictive this assumption
is. The authors claim it is weak just after stating it and then
present several straightforward examples in which it doesn't hold
(e.g. $f(x_1,x_2)=x_1 x_2$) and multivariate Gaussian examples. Hence it is unclear to me how
likely a given function is likely to fit into this framework.}

### 2015-05-15 tex/scam/reviews-v1/response-v1.tex

\subsection*{Reviewer 3}

\begin{enumerate}

\item \rc{I don't see why one would use convex regression to do
  variable screening when other parametric approaches seem more
  appropriate (e.g. clean and screen methods by Ke et al. and
  others). This method and others were compared with and so it again
  raised the question of what class of interesting examples would this
  method be useful for.}

Our methods are appropriate in settings where one expects the
regression function to be convex, for example in utility function
estimation in economics. The power of our framework and analysis is that
using convex additive models leads to consistent variable selection.
In more general settings, without this shape constraint,
approaches based on the lasso (``screen and clean'') or nonparametric 
additive models do not have such guarantees.

@@

\item \rc{The basis of all the results seem to be the boundary flatness
condition. This condition seems to be an artifact of the analysis and
based on my reading, it is unclear how restrictive this assumption
is. The authors claim it is weak just after stating it and then
present several straightforward examples in which it doesn't hold
(e.g. $f(x_1,x_2)=x_1 x_2$) and multivariate Gaussian examples. Hence it is unclear to me how
likely a given function is likely to fit into this framework.}

The boundary flatness condition is not restrictive in the sense that
for any density $p(x)$ supported on $[0,1]^p$, and for any $\epsilon >
0$, there exists a boundary flat density whose $L_1$ distance with
$p(x)$ is at most $\epsilon$. Please see the newly added Example
3.3. This is because boundary flatness places no restriction on what
$p(x)$ looks like in the interior of the hypercube. Boundary flatness
allows arbitrary correlation structure, provided that $p(x) > 0$. We
have added Section 3.2 to the paper to give a more detailed discussion
of boundary flatness.

$f(x_1,x_2) = x_1 x_2$ is non-convex and it is an example of how
non-convex functions may not be additively faithful under the uniform
distribution; it is not an example for which boundary flatness fails
to hold. The multivariate Gaussian counterexample is used to show
that boundary flatness may not extend easily to densities with
unbounded support.

We acknowledge that many distributions are not boundary flat. We
present boundary flatness as a significant generalization of the
product density, under which nonparametric variable selection is
already very difficult (Comminges and Dalalyan, 2012).

### 2015-05-15 tex/scam/summary.tex
defn change

Our first result shows that convex multivariate functions are
additively faithful
under the following assumption on the distribution of the data.
\begin{definition}
  Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$.  Then $p$
  satisfies the \emph{boundary flatness condition} if for all $j$, and
  for all $\mathbf{x}_{-j}$,
\[
\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0
\quad \trm{at $x_j = 0$ and $x_j = 1$}.
\]
\end{definition}

>>>>

Our first result shows that convex multivariate functions are
additively faithful
under the following assumption on the distribution of the data.
\begin{definition}
  Let $p(\mathbf{x})$ be a density supported on $[0,1]^p$. Then $p$
  satisfies the \emph{boundary flatness condition} if it satisfies certain regularity conditions (see precise statement in Definition~\ref{defn:boundary-point}) and if for all $j$, and
  for all $\mathbf{x}_{-j}$,
\[
\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0
\quad \trm{at $x_j = 0$ and $x_j = 1$}.
\]
\end{definition}
